### 2017-07-18 cv-body.tex
Fix en dash
Update CV

\begin{description}
\tightlist
\item[2017]
Aquatic Science Biologist, Offshore Section, Aquatic Resource Research
and Assessment Division, Pacific Biological Station, Fisheries and
Oceans Canada, Nanaimo, BC, Canada
\item[2015--17]
David H. Smith Conservation Research Fellow, School of Aquatic and
Fishery Sciences, University of Washington and Northwest Fisheries
Science Center, Seattle, WA, USA
\item[2015]
Postdoctoral Fellow, School of Resource and Environmental Management,
Simon Fraser University, Burnaby, BC, Canada
\item[2011--15]
Graduate Research Assistant, Department of Biological Sciences, Simon
Fraser University, Burnaby, BC, Canada
\item[2008--11]
Graduate Research Assistant, Department of Biology, Dalhousie
University, Halifax, NS, Canada
\end{description}

@@

@@

@@

Academy of Sciences. 114(12): 3252---3257.

@@

Thorson, J.C. Walsh, M. Dickey-Collas, K.M. Kleisner, C. Longo, G.C.
Osio, D. Ovando, I. Mosqueira, A.A. Rosenberg, E.R. Selig. Improving
estimates of population status and trend with superensemble models. Fish
and Fisheries. In press. \url{http://doi.org/10.1111/faf.12200}.

>>>>

\begin{description}
\tightlist
\item[2017]
Aquatic Science Biologist and Program Head in Spatial Stock Assessment,
Offshore Section, Aquatic Resource Research and Assessment Division,
Pacific Biological Station, Fisheries and Oceans Canada, Nanaimo, BC,
Canada
\item[2015--17]
David H. Smith Conservation Research Fellow, School of Aquatic and
Fishery Sciences, University of Washington and Northwest Fisheries
Science Center, Seattle, WA, USA
\item[2015]
Postdoctoral Fellow, School of Resource and Environmental Management,
Simon Fraser University, Burnaby, BC, Canada
\item[2011--15]
Graduate Research Assistant, Department of Biological Sciences, Simon
Fraser University, Burnaby, BC, Canada
\item[2008--11]
Graduate Research Assistant, Department of Biology, Dalhousie
University, Halifax, NS, Canada
\end{description}

@@

Hughes, B., S. Lummis, \textbf{S.C. Anderson}, K. Kroeker. Unexpected
resilience of a seagrass system exposed to multiple stressors. Global
Change Biology. In press.
Megias, D.A., \textbf{S.C. Anderson}, R.J. Smith, D. Veríssimo.
Investigating the impact of media on demand for wildlife: a case study
of Harry Potter and the UK trade in owls. PLOS ONE. In press.
Chezik, K.A., \textbf{S.C. Anderson}, J.W. Moore. River networks dampen
long-term hydrological signals of climate change. Geophysical Research
Letters. In press. \url{http://doi.org/10.1002/2017GL074376}

@@

\url{http://doi.org/10.1111/conl.12363}

@@

Academy of Sciences. 114(12): 3252--3257.

@@

Thorson, J.C. Walsh, J. Afflerbach, M. Dickey-Collas, K.M. Kleisner, C.
Longo, G.C. Osio, D. Ovando, I. Mosqueira, A.A. Rosenberg, E.R. Selig.
Improving estimates of population status and trend with superensemble
models. Fish and Fisheries. 18(4): 732--741.
\url{http://doi.org/10.1111/faf.12200}
